---
title: "RFinal1"
author: "Kathryn Haglich"
date: "12/13/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(ggmosaic)
library(esquisse)
library(shiny)
library(shinydashboard)

library(readxl)
library(janitor)
library(magrittr)

library(maps)
library(maptools)
library(mapproj)
library(ggmap)

library(leaflet)
library(leaflet.extras)

library(wordcloud)

library(gutenbergr)
library(tidyverse)
library(tidytext)

```

# List of Books Included 
Moby Dick 15 
Peter Pan 16 
The Book of Mormon 17 
Paradise Lost 20 or 26 
Aesop's Fables 28 
The Bible 30 
The Scarlet Letter 33 
The Time Machine 35 
The Legend of Sleepy Hallow 41 
Anne of Green Gables 45
A Christmas Carol 46
Aladdin 57
The Communist Manifesto 61 
The Red Badge of Courage 73
The Adventures of Tom Sawyer 74
The House of the Seven gables 77 
Frankenstein 84 
A Tale of Two Cities 98 
Collected Articles of Frederick Douglass 99 
Around the World in Eighty Days 103 
The Return of Sherlock Holmes 108 
The Secret Garden 113 
Les Miserables 135 
The Jungle 140 
Mansfield Park 141
Common Sense 147 
The Republic 150 
Sense and Sensibility 161
Twenty Thousand Leagues Under the Sea 164
The Picture of Dorian Gray 174 
The Phantom of the Opera 174 
Uncle Tom's Cabin 203
Call of the Wild 215
The Aeneid 228 
The Jungle Book 236 
Myths and Legends of the Sioux 341
Dracula 345
Little Women 514 
The Bobbsey Twins in the Country 714 
Robin Hood 832
White Fang 910 
Beowulf 981
Don Quixote 996 
Divine comedy Longfellow's Translation Complete 1004 
The Tragedy of Romeo and Juliet 1112
Much Ado about Nothing 1118 
The Tragedy of Julius Caesar 1120 
The Tragedy of Hamlet, Prince of Denmark 1122
The Tragedy of Macbeth 1129 
The Prince Machiavelli 1232 

#Code 

```{r choose books you want to focus on, include = FALSE}
booksId = sort(c(999999, 1232, 1129, 1122, 1120, 1118, 1112, 1004, 996, 981, 910, 832, 714, 514, 345, 341, 236, 228, 215, 203, 175, 174, 164, 161, 150, 147, 141, 140, 135, 113, 108, 103, 99, 98, 84, 77, 74, 73, 61, 57, 46, 45, 41, 35, 33, 30, 28, 20, 17, 16, 15))

numBooks = length(booksId)

miniMeta <- gutenberg_metadata %>% filter(gutenberg_id %in% booksId )

bookTitles <-as.vector(miniMeta$title)

bookData <- cbind(booksId, bookTitles)
```

gutenberg_download(id) gets you the book with that id number
also, the index in your id and title vectors correspond 

```{r country cleaning, include = FALSE}
data("world.cities") #data set with lists of cities and countries 

#set up the world data set to use for the latitudes and longitudes 
world <- world.cities %>% 
  rename(country = country.etc) %>% 
  filter(capital == 1)%>% select(-c(pop,capital))

world$country <- tolower(world$country)
world$country[world$country == "korea north"] <- "north korea"
world$country[world$country == "korea south"] <- "south korea"
world$country[world$country == "uk"] <- "united kingdom"
world$country[world$country == "usa"] <- "united states"

newGB <- c("london", "great britain", 	51.52, 	-0.10, 1)
newEngland <- c("london", "england", 	51.52, 	-0.10, 1)
newUS <- c("washington", "united states of america", 38.91, -77.02, 1)
newScotland <- c("edinburgh", "scotland", 55.95, -3.22, 0)
world <- rbind(world, newGB, newEngland, newUS,newScotland)

#list of countries 
countries <- unique(world$country)
```



```{r frequency of places mentioned in book, include = FALSE}

#Case Study: Paradise Lost

gutNum <- 20

 book <- gutenberg_download(gutNum)
 book %<>%
   unnest_tokens(word, text) %>%
   anti_join(stop_words)
 bkCount <-  book %>% count(word, sort = TRUE)


#specific to paradise lost 

bkCountries <- intersect(countries, bkCount$word)#list of countries in book 
bkCountryFreq <- filter(bkCount, word %in% bkCountries) %>%
  rename(country = word) #frequencies of countries 
nameFreq <- paste(bkCountryFreq$country, bkCountryFreq$n, sep = " ")
bkCountryFreq <- cbind(bkCountryFreq, nameFreq)
#data set of country, lat long and frequency specific to book 
bkMini <- world %>% filter(country %in% bkCountries)
bkFull <- left_join(bkMini,bkCountryFreq)

bkFull$lat <- as.double(bkFull$lat)
bkFull$long <- as.double(bkFull$long)

 
#create an interactive map 
leaflet(bkFull)%>%
       setView(lng = 0, lat = 0, zoom = 1)%>%
       addTiles()%>%
       addCircles(data = bkFull, lat = ~lat, lng = ~long, weight = 8, 
                  radius = 300, popup = ~as.character(nameFreq))


```





```{r sentiment analysis, include = FALSE}
# #using the number one to get a measure of positive and negative 
# get_sentiments("afinn")
# 
# #got my book 
# tidyBook <- book %>%
#   mutate(linenumber = row_number()) #%>%
# #  unnest_tokens(word, text)
# 
# 
# tidy_books <- austen_books() %>%
#   group_by(book) %>%
#   mutate(linenumber = row_number()) %>%
#   ungroup() %>%
#   unnest_tokens(word, text)
# 
# 
# 
# bookSentiment <- book %>%
#   inner_join(get_sentiments("afinn")) #%>%
#  # count(book, index = linenumber %/% 80, sentiment) %>%
#  # spread(sentiment, n, fill = 0) %>%
#  # mutate(sentiment = positive - negative)
```

```{r, include = FALSE}
#clean book 
# tidypl <- gutenberg_download(gutNum) %>%
#   unnest_tokens(word, text) %>%
#   anti_join(stop_words)

#word counts 
# tidypl %>%
#   count(word, sort = TRUE)
# 
# af <- get_sentiments("afinn")

# sentimentpl <- tidypl %>%
# #  mutate(linenumber = row_number()) %>%
#   inner_join(get_sentiments("afinn")) #%>%



```



```{r word clouds yay, include = FALSE}
#library(reshape2)
# %>%
 # inner_join(get_sentiments("bing")) %>%
 # count(word, sentiment, sort = TRUE) %>%
 # acast(word ~ sentiment, value.var = "n", fill = 0) %>%
 # comparison.cloud(colors = c("gray20", "gray80"),
  #                 max.words = 100)

bookCloud <- bkCount %>%
  with(wordcloud(word, n, max.words = 100))


```



```{r THE SHINY APP WOOHOO, include=FALSE}
#icon = icon("")
#<i class="fas fa-book-open"></i>

############## USER INTERFACE ##############
ui2 <- dashboardPage(
  dashboardHeader(title = "Literary Analysis"),
  
  dashboardSidebar(
    sidebarMenu(
      radioButtons("option", "What Do You want to Explore?",
               c(
                 "Sentiments" = "sentiment",
                 "Word Cloud" = "cloud",
                 "Maps!" = "maps")),
      
      #selectInput("xVariable", "X Variable", interAll),
      #selectInput("yVariable", "Y Variable", interAll),#ENDS selectInput
      selectInput("book", "Take a look in this book", bookTitles) #ENDS selectInput
      
    )#ENDS sidebarMenu 
  ),#ENDS dashboardSidebar
  
  
   dashboardBody(
     
     mainPanel(leafletOutput("mapPlot"),
               plotOutput("cloudy"))
     #ENDS mainPanel
     
   )#ENDS dashboardBody
)



############## SERVER ##############
server2 <- function(input, output) {
  

######### Sets up the server stuff for the maps ####################
  wordFreqsOfChosen <- reactive({
    bookName = input$book
    #gutenberg id for chosen book 
    gutNum <- bookData[1,bookData$bookTitles == bookName]
    #gets the data for the chosen book 
    chosenBook <- gutenberg_download(gutNum)
    chosenBook %<>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words)
    bkCount <-  chosenBook %>% count(word, sort = TRUE)
    return(bkCount)
  })
  
  countryData <- reactive({ 
    
    bkcount <- wordFreqsOfChosen() #data set of word freqs
    bkCountries <- intersect(countries, bkcount[,2])#list of countries in book 
    
    #isolates countries of interest from word frequency 
    bkCountryFreq <- bkcount %>% filter(word %in% bkCountries) %>%
        rename(country = word) 
    #makes nices labels for the map 
    nameFreq <- paste(bkCountryFreq[,1], bkCountryFreq[,2], sep = " ")
    bkCountryFreq <- cbind(bkCountryFreq, nameFreq)
    
    #finds the countries of interest from main world data set 
    bkMini <- world %>% filter(country %in% bkCountries)
    #combines info from world data set to the frequencies and labels 
    bkFull <- left_join(bkMini,bkCountryFreq)
    
    #makes latitudes and longitudes doubles 
    bkFull$lat <- as.double(bkFull[,3])
    bkFull$long <- as.double(bkFull[,4])
    
    return(bkFull)
    })
  
    finalMap <- reactive({
      if(input$option == "maps"){
      mapData <- countryData()
      theMap <- leaflet(mapData)%>%
       setView(lng = 0, lat = 0, zoom = 1)%>%
       addTiles()%>%
       addCircles(data = mapData, lat = ~lat, lng = ~long, weight = 8,
                  radius = 300, popup = ~as.character(nameFreq))
      return(theMap)
      }
    })
  
  # ERROR: $ operator is invalid for atomic vectors 
     output$mapPlot <- renderLeaflet({ finalMap() })
      
     
######### Sets up the server stuff for the cloud ####################
     makeCloud <- reactive({
       if(input$option == "cloud")
       bookCloud <- wordFreqsOfChosen() %>%
          with(wordcloud(word, n, max.words = 100))
       return(bookCloud)
     })
     
     # ERROR: $ operator is invalid for atomic vectors 
     output$cloudy <- renderPlot({makeCloud()})
     
     
} #ENDS function()


shinyApp(ui2, server2)
    



```




```{r scraped but entertaining paradise lost, include = FALSE}
#### Experimenting ####

#cleaning city names 
#cityList <- tolower(unique(world.cities$name))
#plCities <- intersect(cityList, plCount$word)
 
# plCities <- intersect(cityList, plCount$word)#cities in paradise lost
# plCountries <- intersect(countryList, plCount$word)#countries in paradise lost 


# plCityData <- world.cities %>% 
#   filter(name %in% plCities) %>% #filter by cities mentioned 
#   filter(country.etc %in% plCountries)




#### RANDOM STUFF ####
######### Sets up the server stuff for the question displays ####################
  
  # USunq <- reactive({USUnique[c(1:length(USUnique))]})
  # Japanunq <- reactive({JapanUnique[c(1:length(JapanUnique))]})
  # Russiaunq <- reactive({RussiaUnique[c(1:length(RussiaUnique))]})
  # 
  # intAll <- reactive({interAll[c(1:length(interAll))]})
  # intUSR <- reactive({interUSRus[c(1:length(interUSRus))]})
  # intUSJ <- reactive({interUSJap[c(1:length(interUSJap))]})
  # intRJ <- reactive({interUSJap[c(1:length(interUSJap))]})
  # 
  # allNot <- reactive({allNotAsked[c(1:length(allNotAsked))]})
  # USNot <- reactive({notAskedUS[c(1:length(notAskedUS))]})
  # RNot <- reactive({notAskeRussiaS[c(1:length(notAskedRussia))]})
  # JNot <- reactive({notAskedJapan[c(1:length(notAskedJapan))]})
  
  # chosenSet <- reactive({
  #   if(input$option == "quest"){
  #   
  #     if(input$questVariable == "Unique to US"){return(USunq())}
  #     if(input$questVariable == "Unique to Russia"){return(Russiaunq())}
  #     if(input$questVariable == "Unique to Japan"){return(Japanunq())}
  #   
  #     if(input$questVariable == "Intersection of All Three"){return(intAll())}
  #     if(input$questVariable == "Intersection Between US and Russia"){return(intUSR())}
  #     if(input$questVariable == "Intersection Between US and Japan"){return(intUSJ())}
  #     if(input$questVariable == "Intersection Between Russia and Japan"){return(intRJ())}
  #   
  #     if(input$questVariable == "Not Asked at All"){return(allNot())}
  #    if(input$questVariable == "Not Asked in US"){return(USNot())}
  #    if(input$questVariable == "Not Asked in Russia"){return(RNot())}
  #    if(input$questVariable == "Not Asked in Japan"){return(JNot())}
  #   }
  # })
  
  # output$QuestionSet <- renderTable(chosenSet())

  

    
################ Sets up the server stuff for the graphs displays ####################
  
#setting up what the graphs would be if the user chooses the single variable option   
#   graphUS1 <- reactive({
#     
#     ggplot(US, aes(x=US[,c(input$xVariable)]))+
#       geom_bar() +
#       labs(x = "Chosen Variable", y = "Frequency", title='US')+
#       theme(axis.text.x = element_text(angle = 45, hjust = 1))
#   })
#   graphRussia1 <- reactive({
#     ggplot(data = Russia, aes(x=Russia[,c(input$xVariable)]))+
#       geom_bar() +
#       labs(x = "Chosen Variable", y = "Frequency", title='Russia')+
#       theme(axis.text.x = element_text(angle = 45, hjust = 1))
#     })
#   graphJapan1 <- reactive({ggplot(data = Japan, aes(x=Japan[,c(input$xVariable)]))+
#       geom_bar() +
#       labs(x = "Chosen Variable", y = "Frequency", title='Japan')+
#       theme(axis.text.x = element_text(angle = 45, hjust = 1))
#     })
#   
# 
#   #setting up what the graphs would be if the user chooses the double variable option 
#    graphUS2 <- reactive({
#       ggplot(US, aes(x=US[,c(input$xVariable)], fill = US[,c(input$yVariable)]) ) +
#       geom_bar(position = "fill") +
#       scale_fill_viridis_d(option = "viridis") +
#        labs(x = "Chosen X Variable", y = "Frequency", title='US', fill = "Chosen Y Variable")+
#       theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
#   })
#    graphRussia2 <- reactive({
#    ggplot(Russia, aes(x=Russia[,c(input$xVariable)], fill = Russia[,c(input$yVariable)]) ) +
#       geom_bar(position = "fill") +
#       scale_fill_viridis_d(option = "viridis") +
#        labs(x = "Chosen X Variable", y = "Frequency", title='Russia', fill = "Chosen Y Variable")+
#       theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")
# 
#   })
#    
#    graphJapan2 <- reactive({
#    ggplot(Japan, aes(x=Japan[,c(input$xVariable)], 
#                      fill = Japan[,c(input$yVariable)]) ) +
#       geom_bar(position = "fill") +
#       scale_fill_viridis_d(option = "viridis") +
#        labs(x = "Chosen X Variable", y = "Frequency", title='Japan', fill = "Chosen Y Variable")+
#       theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
#   })
#   
#   chosenUSGraph <- reactive({
#     if(input$option == "single"){return(graphUS1())}
#      if(input$option == "double"){return(graphUS2())}
#   })
#   
#   chosenRussiaGraph <- reactive({
#     if(input$option == "single"){return(graphRussia1())}
#      if(input$option == "double"){return(graphRussia2())}
#   })
#   
#   chosenJapanGraph <- reactive({
#     if(input$option == "single"){return(graphJapan1())}
#      if(input$option == "double"){return(graphJapan2())}
#   })
#   
# 
# ### Prints out the graphs 
#   output$USgraph <- renderPlot({chosenUSGraph()})
#   output$Russiagraph <- renderPlot({chosenRussiaGraph()})
#   output$Japangraph <- renderPlot({chosenJapanGraph()})
#   
  
#} #ENDS function()

#ENDS dashboardPage

  #    mainPanel(tableOutput("QuestionSet"),
  #      fluidRow(splitLayout(style = "border: 1px solid silver:", cellWidths = c(300,300,300), 
  #                            plotOutput("USgraph"),
  #                           plotOutput("Russiagraph"),
  #                            plotOutput("Japangraph")
  #                            )#ENDS splitLayout
  #                          )#ENDS fluidRow
  #               )#ENDS mainPanel 
  # 

  
```







